---
title: "feature-transformation"
author: "ogorodriguez"
date: "2020-12-10"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


```{r}
# Setting global options
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.path = "data/images",
                      fig.width = 12,
                      fig.height = 8)
```

```{r}
# Installing packages
pacman::p_load(tidyverse,
               here,
               lubridate,
               tidytext,
               tidyr,
               caret,
               janitor,
               dplyr)
```

## Feature Transformation

In this section we will use the `purrr` package that has functions for recursive operations, iteration, and the like.

Here, we will do a feature transformation, which means, we will alter the value of the variables (columns)
by applying a function to each of them.

This is sometimes useful when trying to analyse data that is heavily skewed in trying to have a more normal distribution
for ease of analysis.  In this case we will just simply apply a function to all the variable columns and save them in our 
nested data frame to see how we can preserve the integrity of the data all within one single object (the nested df)

A function will be created that will obtain the power of all numerical values in our nested data frame.

Since we have for copies of our data frame now, we will create a function that will apply four different 
powers, one to each of our nested df's. This will be applicable to all numeric variables (aka features) of our dataframe. 

```{r}
# function to apply a given power (power-transformation) to numerical (dbl) columns in our dataframe
power_transf <- function(dframe, power) {
  dframe %>% 
    mutate_if(~ is.numeric(.x),
              ~ `^`(.x, power)) %>% 
    select(-item, -category)
}

```

The `purrr` package has the `map` tool that will be the power horse of the iteration.
It will go over every data frame in our nested object and will get the power of each column
to the value that we assign to the variable power.

To keep track of the power applied we will create a new list-column data frame with two
new columns:

  _power_: to know which power was applied for the transformation
  **tms_data**: which is the new data frame with the power transformation applied.
  
Our nested list-column set `menu_nest` will have a new column called power.  We will need to use the `map2` function
So it applies to both the new power column and the data column of the original `menu_nest` df.  
A new column called label will be added as well.

```{r}
# add 3 columns to menu_nest: power, transf_data, and label
menu_nest <- read_rds("data/menu_nest.rds")
menu_transf <- menu_nest %>% 
  mutate(
    power = c(0.5, 1, 2, 3),
    transf_data = purrr::map2(data, power, ~ power_transf(.x, .y)),
    label = purrr::map(data, "category")
  )

menu_transf

```

The new `menu_transf` data frame holds our original list-column data frame, the transformed ones 
from each power associated, a column that tells us which power is being applied and also
a column that indicates the category of the food being analysed.

This was just a simple example.  The same type of workflow is required when applying
maching learning algorithms to our nested dataframe.

In the next section, instead of using a user-defined function, we will use the functions in caret.
caret is a package for machine learning algorithms.








































































