---
title: "Introduction"
author: "ogorodriguez"
date: "2020-12-10"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r}
# Setting global options
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.path = "data/images",
                      fig.width = 12,
                      fig.height = 8)
```

```{r}
# Installing packages
pacman::p_load(tidyverse,
               here,
               lubridate,
               tidytext,
               tidyr,
               caret,
               janitor,
               dplyr)
```


## Introduction

This notebook will review the nested workflow used by Jared Wilber [in his website](https://www.jwilber.me/nest).  

The main objective is to use the data frame as the object to hold all elements of the data analysis.  
That is, besides data, the data frame will also hold parameters, and other objects as well that will help carry 
all elements together and avoid repetition.  

This is important for me since I believe that having everything at close range and already tidy for
work I believe will help improve my workflow and make me more efficient in my learning and analysis.

Some reasons why this approach may facillitate the analysis:

  * It provides an easy mental model to work with data
  * All related objects are stored together
  * Reduces clutter
  * There is consistency in the data arrangement and will help in further analysis
  
For this analysis, the McDonalds US Nutrition facts menu data set will be used to do some basic
machine learning workflow analysis.  [It can be found in Kaggle here.](https://www.kaggle.com/mcdonalds/nutrition-facts)































```{r}

```

