---
title: "feature-transformation"
author: "ogorodriguez"
date: "2020-12-10"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


```{r}
# Setting global options
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.path = "data/images",
                      fig.width = 12,
                      fig.height = 8)
```

```{r}
# Installing packages
pacman::p_load(tidyverse,
               here,
               lubridate,
               tidytext,
               tidyr,
               caret,
               janitor,
               dplyr)
```

## Machine Learning Algorithms

We will create a list column of all the machine learning algorithms we are going to apply to our for transformed (normalized) data sets for each of their transformations or powers used.

The caret package has different algorithm implementations within a consistent API.  We will create a machine learning function factory.

```{r}
# maching learning model function factory
ml_fun_fact <- function(ml_method) {
  function(data, label) {
    caret::train(
      x = data,
      y = label,
      method = ml_method
    )
  }
}

```

## Creating the data frame for our algorithm

Now we will create the data frame that will host all of our functions.


  
```{r}
model_df <- list(
  decision_tree = ml_fun_fact("rpart2"),
  random_forest = ml_fun_fact("ranger"),
  boosted_log_reg = ml_fun_fact('LogitBoost'),
  knn = ml_fun_fact('knn'),
  svm = ml_fun_fact('svmLinear3'),
  lda = ml_fun_fact('lda')
  ) %>% 
  enframe(name = "model", value = "model_func")

model_df
```
  

```{r}
write_rds(model_df, "data/model_df.rds")
```






















