---
title: "Tidy Data Review"
author: "ogorodriguez"
date: "2020-12-10"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r}
# Setting global options
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.path = "data/images",
                      fig.width = 12,
                      fig.height = 8)
```

```{r}
# Installing packages
pacman::p_load(tidyverse,
               here,
               lubridate,
               tidytext,
               tidyr,
               caret,
               janitor,
               dplyr)
```

## Review of Tidy Data

A quick recap of what tiday data is.  Tidy data aims to present data in a way that 
every observation is located in one row and all variables are located in each in one column.
Each observation must be hosted in a single cell.

This is a very rectangular data approach to analysis and modeling.  It helps in consistency.
To arrive to such structure, a good knowledge of the data to analyse as well as its normalisation 
is required.

This provides an intuitive mental model for analysis.  

The data set to use to practice the nested approach workflow for analysis and modeling is the 
McDonalds Nutrition facts menu.  The objective is to see if we can predict the items category:
_Breakfast, Desserts, Snacks & Sides_,etc from its nutritional context

### Loading the data

I have already downloaded a copy of the set from Kaggle that I will incorporate to this notebook.

```{r}
# Loading data from data folder.  We will remove non-nutritional content.  
# I will keep the Item to know which product falls unde that category
library(dplyr)
menu <- read_csv("data/raw/menu.csv") %>% 
  clean_names() %>% 
  select(- serving_size)

menu %>% glimpse()

```

Our menu data frame has 260 observations and 23 variables.  

In this notebook, four transformations will be done to the data frame, so we will create four versions
of the menu data set that will be all collected within one single data frame.  

For that we will use nesting functions that will help create list columns.  List columns help us host other objects
in a data frame.  We will create index columns to identify each copy of our data frame.

```{r}
# nest original data frame and make four copies
menu_nest <- rep(list(menu), 4) %>% 
  enframe(name = "index", value = "data")

menu_nest
```

We will need to save the menu_nest and menu data frames for used later

```{r}
write_rds(menu, "data/menu.rds")
write_rds(menu_nest, "data/menu_nest.rds")
```


















































